Wigglyhedra

### 2024-06-26 draft/wigglyhedra.tex
Finished proof of why both outside edges don't appear.

  \(T\) cannot contain both external edges because otherwise, the curve \(\alpha\) will not be able to have a second endpoint.\asilata{I am struggling to explain this, even though it should be obvious.}
\end{proof}

>>>>

  Now suppose for contradiction that \(T\) contains both external edges.
  Then some portion of \(\alpha\) curves around each of the extreme endpoints \(0\) and \(n+1\).
  Consider the outermost strands of \(\alpha\) that curve around \(0\) and \(n+1\) respectively.
  These must then connect to each other, resulting in \(\alpha\) having a separate component that winds around the outside of the \(n+2\) points.
  This is not possible because \(\alpha\) is a connected curve with two endpoints.
  Therefore \(T\) cannot contain both external edges.
\end{proof}
